The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-04-14 paper.tex
subsection{Landmark Line Regions and Measurements}
Fix underscores.

  \item ANNOdc (\cref{sec:core}, \cref{fig:core}) is a domain-core (dc) ontology to provide the core entities of a domain, such as, inter alia, 
the general anatomical categories (\aurl{anno}{Anatomical_structure} and \aurl{anno}{Landmark}), categories for describing different characteristics of 
landmarks (\aurl{anno}{Landmark_location}, \aurl{anno}{Landmark_property} and \aurl{anno}{Landmark_line_region}) as well as 
the category \aurl{anno}{Phenotype} to model the rules for determining human phenotypes. The ANNOdc is founded by \emph{General Formal Ontology} (GFO)~\citep{gfo}.

@@

In ANNO, we consider bone structures and teeth as anatomical structures relevant to the anthropology domain. 
Bone structures are divided into single bones and bone compounds consisting of further bones (has_part). 
Teeth are located on bone structures (on_bone).

@@

\subsection{Landmark Line Regions and Measurements}
Landmark line regions are lines connecting or outlining landmarks (e.g., an edge between two landmarks, an angle between three landmarks 
or an outline of one or more landmarks).
The landmark line regions can be measured (e.g., the length of the edge or outline and the angle degree).
Such measurements can be used to derive/determine individual phenotypes.

>>>>

  \item ANNOdc (\cref{sec:core}, \cref{fig:core}) is a domain-core (dc) ontology to provide the core entities of a domain, such as, inter alia, 
the general anatomical categories (\aurl{anno}{Anatomical\_structure} and \aurl{anno}{Landmark}), categories for describing different characteristics of 
landmarks (\aurl{anno}{Landmark\_location}, \aurl{anno}{Landmark\_property} and \aurl{anno}{Landmark\_line\_region}) as well as 
the category \aurl{anno}{Phenotype} to model the rules for determining human phenotypes. The ANNOdc is founded by \emph{General Formal Ontology} (GFO)~\citep{gfo}.

@@

In ANNO, we consider bone structures and teeth as anatomical structures relevant to the anthropology domain. 
Bone structures are divided into single bones and bone compounds consisting of further bones (has\_part). 
Teeth are located on bone structures (on\_bone).

@@

\subsection{Landmark Line Regions and Measurements}
Landmark line regions are lines connecting or outlining landmarks (e.g., an edge between two landmarks, an angle between three landmarks 
or an outline of one or more landmarks). A landmark line region can start on one landmark and end on another, 
passing through or bordering multiple landmarks.
The landmark line regions can be measured (e.g., the length of the edge or outline and the angle degree).
Such measurements can be used to derive/determine individual phenotypes.
